\subsubsection{GNSS Metadata}

The format of the GNSS location block is described in figure \ref{format:telem-gnss-metadata}. The length of this block
varies, after the GLONASS satellites in use bit field 4 bytes of information is encoded for each satellite in view of
the GNSS module. Note that not all satellites which are in view will also be in use.

\begin{figure}[H]
    \centering
    \begin{bytefield}[bitwidth=0.03\linewidth]{32}
        \bitheader{0-31} \\
        \wordbox{1}{Mission Time} \\
        \wordbox{1}{GPS Satellites in Use} \\
        \wordbox{1}{GLONASS Satellites in Use} \\
        \begin{rightwordgroup}{First Sat}
            \bitbox{8}{Elevation} & \bitbox{8}{SNR} & \bitbox{5}{ID} &
            \bitbox{9}{Azimuth} &
            \bitbox{1}{\color{lightgray}\rule{\width}{\height}} &
            \bitbox{1}{T}
        \end{rightwordgroup} \\
        \bitbox[]{32}{$\vdots$ \\[1ex]} \\
        \begin{rightwordgroup}{Last Sat}
            \bitbox{8}{Elevation} & \bitbox{8}{SNR} & \bitbox{5}{ID} &
            \bitbox{9}{Azimuth} &
            \bitbox{1}{\color{lightgray}\rule{\width}{\height}} &
            \bitbox{1}{T}
        \end{rightwordgroup}
    \end{bytefield}
    \caption{GNSS Metadata Payload Format}
    \label{format:telem-gnss-metadata}
\end{figure}

\paragraph{Mission Time}
The mission time when the fix was received.

\paragraph{GPS Satellites in Use}

This bit field indicates which GPS satellites are used in the current fix. Each bit position represents a GPS
pseudo-random noise sequence.

\paragraph{GLONASS Satellites in Use}
This bit field indicates which GLONASS satellites are used in the current fix. Each bit position represents a slot
number. Bit zero corresponds to slot 65, bit 1 to slot 66 and so on.

\paragraph{Elevation}
This field represents the elevation for a GNSS satellite in degrees.

\paragraph{SNR}
This field represents the signal to noise ratio for a signal from a satellite in dB Hz.

\paragraph{ID}
This field contains the satellite pseudo-ransom noise sequence for GPS satellites or the satellite ID for GLONASS
satellites.

\paragraph{Azimuth}
This field contains the satellite azimuth in degrees.

\paragraph{T}
This field encodes the satellite type, it is 0 for GPS satellites or 1 for GLONASS satellites.

