\subsubsection{GNSS Location}

The format of the GNSS location block is described in figure \ref{format:telem-gnss-location}.

\begin{figure}[h]
    \centering
    \begin{bytefield}[bitwidth=0.03\linewidth]{32}
        \bitheader{0-31} \\
        \wordbox{1}{Fix Time} \\
        \wordbox{1}{Latitude} \\
        \wordbox{1}{Longitude} \\
        \wordbox{1}{UTC Time} \\
        \wordbox{1}{Altitude} \\
        \bitbox{16}{Speed} & \bitbox{16}{Course} \\
        \bitbox{16}{PDOP} & \bitbox{16}{HDOP} \\
        \bitbox{16}{VDOP} & \bitbox{8}{Sats} & \bitbox{2}{Fix} &
        \bitbox{6}{\color{lightgray}\rule{\width}{\height}}

    \end{bytefield}
    \caption{GNSS Location Data Payload Format}
    \label{format:telem-gnss-location}
\end{figure}

\paragraph{Fix Time}
The mission time when the fix was received.

\paragraph{Latitude}
The latitude of the rocket in units of \SI{100}{\micro\arcminute\per LSB} (micro-arcminutes per least significant bit).
This field is a signed 32 bit integer in two's complement format.

\paragraph{Longitude}
The longitude of the rocket in units of \SI{100}{\micro\arcminute\per LSB} (micro-arcminutes per least significant
bit). This field is a signed 32 bit integer in two's complement format.

\paragraph{UTC Time}
The UTC time when the fix was received in seconds since the Unix epoch.

\paragraph{Altitude}
The altitude as calculated by the GNSS module in units of millimetres above sea level. This field is a signed 32 bit
integer in two's complement format.

\paragraph{Speed}
The speed over ground of the rocket in hundredths of a knot. This field is a signed 16 bit integer in two's complement
format.

\paragraph{Course}
The course over ground of the rocket in hundredths of a degree. This field is a signed 16 bit integer in two's
complement format.

\paragraph{PDOP}
Position Dilution of Precision * 100.

\paragraph{HDOP}
Horizontal Dilution of Precision * 100.

\paragraph{VDOP}
Vertical Dilution of Precision * 100.

\paragraph{Sats}
The number of GNSS satellites used in the fix.

\paragraph{Fix}
The fix type as shown in table \ref{table:gnss-fix-type}.

\begin{table*}[htb]
    \centering
    \begin{tabular}{@{}ll@{}}
        \toprule
        Fix Type Value & Description   \\
        \midrule
        0x0            & Unknown       \\
        0x1            & Not available \\
        0x2            & 2D fix        \\
        0x3            & 3D fix        \\
        \bottomrule
    \end{tabular}
    \caption{GNSS Fix Type Values}
    \label{table:gnss-fix-type}
\end{table*}
