\subsubsection{Signal Report}

A signal report contains information designed to allow the recipient to assess the quality of the radio link. Signal
reports may be sent at any time by any party and should contain information pertaining to the last packet received from
the block's destination device.

Signal reports follow a query response structure. An initial signal report that is marked as a request is sent first.
The recipient of this request then responds with a signal report that is not marked as a request.

The format of the payload data for a signal report is described in figure \ref{format:signal-report}.

\begin{figure}[H]
    \centering
    \begin{bytefield}[bitwidth=0.03\linewidth]{32}
        \bitheader{0-31} \\
        \bitbox{8}{SNR} & \bitbox{8}{RSSI} & \bitbox{2}{\tiny{Radio}} &
        \bitbox{6}{TX Power} \bitbox{7}{\color{lightgray}\rule{\width}{\height}} &
        \bitbox{1}{\rotatebox{90}{\tiny{Req.}}}
    \end{bytefield}
    \caption{Signal Report Payload Format}
    \label{format:signal-report}
\end{figure}

\paragraph{SNR}
Signal to Noise Ratio for the last packet received from the destination device in units of \SI{1}{\decibel\per LSB}.
This value is encoded as a one byte signed integer in twos compliment format.

In a response signal report this should always be the SNR for the packet that contained the request.

\paragraph{RSSI}
Received Signal Strength Indication for the last packet received from the destination device in units of
\SI{1}{\decibel\per LSB}. This value is encoded as a one byte signed integer in twos compliment format

In a response signal report this should always be the RSSI for the packet that contained the request.

\paragraph{Radio}
The index of the radio used by the device that send the requesting signal report. This field is not meaningful to the
recipient of the request, the recipient simply echos it back to the sender of the request in the response signal
report. This field is encoded as a two bit unsigned integer.

\paragraph{TX Power}
The transmit power with which the packet containing the signal report block was sent in units of \SI{1}{\decibel\per
    LSB}. This value is encoded as a six bit signed integer in twos compliment format

\paragraph{Request}
When set, this bit indicates that this is a request signal report and that the receiver should respond. If this bit is
not set then this block is a response signal report.
